### 2024-02-18 documentation/thesis/thesis_document.tex
.

The Halbach magnetic array appears as an essential element for future
Magnet characterisation. Based on this fact this thesis centres on
assessing the sensors' applicability, the Halbach magnetic array serves
as a tool for later measurements, although its implementation and
further discussion will not be the primary focus.

@@

Within the research domain, various implementations have emerged. An
exemplar instance is the work by O'Reilly, Teeuwisse, and Webb, who
introduced a groundbreaking ``three-dimensional \gls{mri} in a
homogeneous \emph{27cm} diameter Bore Halbach Array magnet''
\customcite{OTW19} in 2019.This innovative setup is subsequently employed
in 2020 to acquire in vivo MR images, showcasing the practical
applications of their pioneering research \customcite{OTW21}. In 2023, de
Vos, Remis and Webb published a summary of the design of a point-of-care
Halbach array low-field \gls{mri} system \customcite{DRW23}.

Within the research domain, various implementations came up. An exemplar
instance is the work by O'Reilly, Teeuwisse, and Webb, who introduced a
groundbreaking ``three-dimensional \gls{mri} in a homogeneous 27cm
diameter Bore Halbach Array magnet'' \customcite{OTW19} in 2019. This
innovative setup is subsequently employed in 2020 to acquire in vivo MR
images, showcasing the practical applications of their pioneering
research \customcite{OTW21}. In 2023, de Vos, Remis and Webb published a
summary of the design of a point-of-care Halbach array low-field
\gls{mri} system \customcite{DRW23}.

The Halbach magnet incorporated in this system boasts a \emph{27cm}
diameter, a \emph{B0} field strength of 50.4mT, and an impressive
homogeneity of \emph{2400 \gls{ppm}} over a \emph{20cm} diameter using
smaller magnets (\(12 x 12 x 12 mm^3\)). This exceptional homogeneity
enables the utilization of coil-based gradients for spatial encoding,
significantly enhancing the flexibility of image acquisition.

@@

To further refine the magnet's homogeneity, optimisation techniques are
employed by adjusting the radius of the Halbach ring along the length of
the magnet. The deliberate choice of smaller magnets, as opposed to
other Halbach designs, serves to compensate for inherent manufacturing
imperfections in each individual magnet. This strategic decision not
only mitigates structural demands on the magnet housing in terms of
strength and weight but also augments safety throughout the construction
process.

@@

The application of the developed framework for the characterisation of
different magnets and the integration of various available magnetic
field sensors serve the practical application and validation of the
developed solution.

@@

\begin{itemize}
\item
  Sensor characterisation: Can the carefully selected sensors
  effectively measure a magnet? Specifically, this involves
  investigating the saturation of the sensors, the linearity of field
  strength concerning distance from the sensor, and, in a subsequent
  phase, exploring temperature dependence.
\item
  Homogeneity Measurement: Can the chosen sensors be adeptly utilized to
  measure the homogeneity of a Halbach ring-based B0 field within the
  stringent limit of less than \emph{1000 \gls{ppm}}? The desired
  outcome is a measurement of less than \emph{50} \(\mu\)T at \emph{1000
  \gls{ppm}}, with a specific focus on determining the sensors'
  viability for noise measurements.
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  *.dump()` - \gls{json}
\item
  \emph{.to\_numpy\_matrix()} - \emph{Numpy}-Array of \emph{data} object
  with different options
\item
  \emph{.dump\_savemat()} - \emph{MATLAB} mat-file with measurement
  values and temperatures
\end{itemize}

@@

\begin{lstlisting}[language=Python, caption={setup.py with dynamic requirement parsing using a given requirements.txt}, label=lst:setup_py_req]
# dynamic requirement loading using 'requirements.txt'
req_path = './requirements.txt'
with pathlib.Path(req_path).open() as requirements_txt:
  install_requires = [str(requirement) for requirement in pkg_resources.parse_requirements(requirements_txt)]

@@

\hypertarget{use-case-evaluation}{%
\chapter{Use Case Evaluation}\label{use-case-evaluation}}

@@

\begin{itemize}
\tightlist
\item
  Plot of the raw data of the sensor
\item
  Plot of the sensor's internal temperature sensor
\item
  Background noise level with reference to the initial baseline
\item
  Histogram of the background noise level
\end{itemize}

>>>>

The Halbach magnetic array appears as an essential element for future
Magnet characterisation. Based on this fact this thesis centres on
assessing the sensors applicability, the Halbach magnetic array serves
as a tool for later measurements, although its implementation and
further discussion will not be the primary focus.

@@

Within the research domain, various implementations have emerged. An
exemplar instance is the work by O'Reilly, Teeuwisse, and Webb, who
introduced a groundbreaking three-dimensional \gls{mri} in a homogeneous
\emph{27cm} diameter Bore Halbach Array magnet \customcite{OTW19} in
2019.This innovative setup is subsequently employed in 2020 to acquire
in vivo MR images, showcasing the practical applications of their
pioneering research \customcite{OTW21}. In 2023, de Vos, Remis and Webb
published a summary of the design of a point-of-care Halbach array
low-field \gls{mri} system \customcite{DRW23}.

@@

To further refine the magnets homogeneity, optimisation techniques are
employed by adjusting the radius of the Halbach ring along the length of
the magnet. The deliberate choice of smaller magnets, as opposed to
other Halbach designs, serves to compensate for inherent manufacturing
imperfections in each individual magnet. This strategic decision not
only mitigates structural demands on the magnet housing in terms of
strength and weight but also augments safety throughout the construction
process.

@@

The application of the develox field sensors serve the practical
application and validation of the developed solution.

@@

\begin{itemize}
\item
  Sensor characterisation: Can the carefully selected sensors
  effectively measure a magnet? Specifically, this involves
  investigating the saturation of the sensors, the linearity of field
  strength concerning distance from the sensor, and, in a subsequent
  phase, exploring temperature dependence.
\item
  Homogeneity Measurement: Can the chosen sensors be adeptly utilized to
  measure the homogeneity of a Halbach ring-based B0 field within the
  stringent limit of less than \emph{1000 \gls{ppm}}? The desired
  outcome is a measurement of less than \emph{50} \(\mu\)T at \emph{1000
  \gls{ppm}}, with a specific focus on determining the sensors viability
  for noise measurements.
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  *.dump() - \gls{json}
\item
  \emph{.to\_numpy\_matrix()} - \emph{Numpy}-Array of \emph{data} object
  with different options
\item
  \emph{.dump\_savemat()} - \emph{MATLAB} mat-file with measurement
  values and temperatures
\end{itemize}

@@

\begin{lstlisting}[language=Python, caption={setup.py with dynamic requirement parsing using a given requirements.txt}, label=lst:setup_py_req]
# dynamic requirement loading using requirements.txt
req_path = './requirements.txt'
with pathlib.Path(req_path).open() as requirements_txt:
  install_requires = [str(requirement) for requirement in pkg_resources.parse_requirements(requirements_txt)]

@@

\hypertarget{haluation}{%
\chapter{Haluation}\label{haluation}}

@@

\begin{itemize}
\tightlist
\item
  Plot of the raw data of the sensor
\item
  Plot of the sensors internal temperature sensor
\item
  Background noise level with reference to the initial baseline
\item
  Histogram of the background noise level
\end{itemize}
